Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2017-04-26 teaching.tex
start 4-player case

>>>>

\vskip.5in
\section{4-player version, Reunification better than Status Quo}
Now we look at the full version of the model including the international community, and continue to assume that the payoffs for the secessionists are lower in the unrecognized state ('Status Quo') than they are if they cede and rejoin the home state.
